Awareness and Russell's Epistemology

### 2011-01-27 simple_justification.tex
changing motivation for sjl

In this section we consider a simplified form of JL suitable for reasoning
over multiple knowledge bases, which we call \tmtextit{simple justification
logic} (SJL). However, instead of thinking of terms as representing proofs, we
use them to represent knowledge bases. This is in the spirit of JL as a logic
of evidence: we consider each knowledge base to be a corpus of evidence. \
Each term ``names'' a different knowledge base at a particular world.  Terms
may not refer to the same knowledge base at different worlds, just as in how
in awareness logic the agent need not be aware of the same formulae at
different worlds.  Finally, we will make use of JL's {\tmem{choice}} operator
as a mechanism for forming the union of knowledge bases, creating new ones.

>>>>

We propose a stripped down, simplified form of JL suitable for reasoning
over multiple knowledge bases, which we call \tmtextit{simple justification
logic} (SJL). % However, instead of thinking of terms as representing proofs, we
% use them to represent knowledge bases. This is in the spirit of JL as a logic
% of evidence: we consider each knowledge base to be a corpus of evidence. \
% Each term ``names'' a different knowledge base at a particular world.  Terms
% may not refer to the same knowledge base at different worlds, just as in how
% in awareness logic the agent need not be aware of the same formulae at
% different worlds.
We will only make use of JL's {\tmem{choice}} operator,
and use it as a mechanism for forming the union of awareness sets, creating new ones.
